\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-14 paper.tex
final conclusion graf, proofs

It is well appreciated by experts and end-users alike that strong authentication is
critical to cybersecurity and privacy, now and into the future. Unfortunately,
news reports of celebrity account hackings serve as regular reminders that
single-factor authentication using passwords or other user-chosen secrets, 
the currently dominant method of authentication in consumer applications, 
face many challenges. Major industry players such as Google and
Facebook have strongly encouraged their users to adopt two-factor
authentication (2FA). However, the need for users to submit two different 
authenticators in two separate steps has frustrated wide adoption, 
due its additional hassle cost to the users. For instance, the popular Apple
iPhone has already implemented the necessary technologies to support device
unlock using either a user-selected passcode or a fingerprint. The
device could easily support a two-step two-factor authentication scheme if
desired. However, it is easy to understand why users would balk at having to
enter a passcode \emph{and} provide a fingerprint each time they want to unlock their phone.

In previous work, "one-step two-factor authentication" has been proposed as a
new approach to authentication that can provide the security benefits of two-
factor authentication without incurring the hassle costs of two-step verification.
By employing consumer-grade EEG (electroencephalogram) sensing
technologies, it was demonstrated in a 2013 passthoughts study that a user can
submit both a knowledge factor (i.e., secret thought) and an inherence factor
(i.e., brainwave signal unique to the individual) in a single step by performing a
single mental task \cite{Chuang2014}. Additionally, the robustness of this method against
impersonation attacks was demonstrated, including conditions where the attacker
may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.

@@

@@

% We provide cursory evidence that passthoughts are difficult to spoof, though further work should expand on ours with more subjects.
Another important question surrounds how passthoughts might be cracked.
Generally, we do not understand how an individual's passthought is drawn from the general distribution of EEG signals that an individual produces throughout the day.
Given a large enough corpus of EEG data, are some passthoughts as easy to guess as \textit{password1234} is for passwords?
Future work should perform statistical analysis on passthoughts, such as clustering (perhaps with t-SNE) to better understand the space of possible passthoughts.
This work will allow us simulate cracking attempts, and to develop empirically motivated strategies for prevention, e.g. locking users out after a certain number of attempts.
This work could also reveal interesting tradeoffs between the usability and accuracy of certain passthoughts with their security properties.

>>>>

It is well appreciated by experts and end-users alike that strong authentication is
critical to cybersecurity and privacy, now and into the future. Unfortunately,
news reports of celebrity account hackings serve as regular reminders that
single-factor authentication using passwords or other user-chosen secrets, 
the currently dominant method of authentication in consumer applications, 
face many challenges. Major industry players such as Google and
Facebook have strongly encouraged their users to adopt two-factor
authentication (2FA). However, submitting two different 
authenticators in two separate steps has frustrated wide adoption
due to its additional hassle cost to users. The Apple iPhone, for instance,
already supports device unlock using either a user-selected passcode or a fingerprint. The
device could easily support a two-step two-factor authentication scheme if
desired. However, it is easy to understand why users would balk at having to
enter a passcode \emph{and} provide a fingerprint each time they want to unlock their phone.

In previous work, "one-step two-factor authentication" has been proposed as a
new approach to authentication that can provide the security benefits of two-
factor authentication without incurring the hassle of two-step verification.
By employing consumer-grade EEG (electroencephalogram),
it was demonstrated in a 2013 passthoughts study that a user can
submit both a knowledge factor (i.e., secret thought) and an inherence factor
(i.e., brainwave signal unique to the individual) in a single step by performing a
single mental task \cite{Chuang2014}. Additionally, the robustness of this method against
impersonation attacks was demonstrated, including conditions where the attacker
may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.

@@

We find that we can achieve low FARs and FRRs with a single, three-electrode earpiece.
Interestingly, we found that we performed better in the ear than on the scalp.
Additionally, we find that an passthoughts could not be spoofed by imposters, even when the imposters had the subject's earpiece and knew the secret passthoughts.
We discuss the benefits of passthoughts to usable authentication, and raise questions about how and why passthoughts work as well as they do.

@@

% We provide cursory evidence that passthoughts are difficult to spoof, though further work should expand on ours with more subjects.
Another important question surrounds how passthoughts might be cracked.
Generally, we do not understand how an individual's passthought is drawn from the distribution of EEG signals that an individual produces throughout the day. 
Given a large enough corpus of EEG data, are some passthoughts as easy to guess as \textit{password1234} is for passwords?
Future work should perform statistical analysis on passthoughts, such as clustering (perhaps with t-SNE) to better understand the space of possible passthoughts.
This work will allow us simulate cracking attempts, and to develop empirically motivated strategies for prevention, e.g. locking users out after a certain number of attempts.
This work could also reveal interesting tradeoffs between the usability and accuracy of certain passthoughts with their security properties.
